Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework

### 2019-05-01 paper/main.tex
Minor changes suggested by Dad

Precoding matrices obtained from SVD of the MIMO channel matrix (which is estimated at the receiver) can be utilized at the transmitter for optimum power allocation and lower BER transmissions. 
A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
Since the bit budget for such channel state information (CSI) feedback is limited, these precoders need to be quantized effectively using just a few bits.
For a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), this amounts to quantizing a $N_T \times N_R$ complex-valued matrix.
This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
Predictive quantization methods reduce the quantization error by predicting new precoders based on observation of past precoders, and then quantizing the information required to obtain the actual precoder from the predicted value. 
In this work, we introduce a reservoir computing based framework for predictive quantization by exploiting temporal correlations. 
Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure for precoder prediction.
Here, this non-linear relationship is captured using the dynamical reservoir state as part of the online training process of the reservoir.
Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.
\end{abstract}

\section{\textbf{Introduction}}
\label{intro}
% Broad summary of your work, come to your problem definition.
In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ antennas of the transmitter.
The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
The MIMO channel matrix is estimated at the receiver, and the transmitter has no a priori knowledge of the same.
Therefore, to obtain the said benefits of SVD precoders at the transmitter, the receiver needs to quantize and feed back the precoders it obtains from the SVD of MIMO channel matrix.
To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
Given the high dimensionality of precoders (which form a $N_T \times N_R$ complex-valued matrix, viz. $2N_TN_R$ real numbers), effective quantization with just a few bits poses a significant challenge.

% Elaborate on each point (what people have done before) lecunnas
Past work has used two inherent properties of the precoders to enable effective quantization with just a few bits.
First, the precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with lower dimensions, when performing operations over the manifold directly.
Second, these precoders are correlated in both time and frequency.
Utilizing these correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
This improvement is obtained because utilizing the available correlations allow for quantization of just the small extra information needed on top of the past fed back estimates, for estimation of the new precoder, as compared to quantization of the complete new precoder information in the entirety.
Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
Combining the two inherent properties (viz. manifold structure and correlations), requires a generalization of various well known linear algorithms for prediction, quantization and interpolation, to the manifold structure under consideration. This is done by exploiting the underlying non-linear differential geometry of the manifold. Relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry,chang2011adaptive}.

% What is the way ahead
Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
However, these approaches are non-trivial, since they require specific operations over the non-linear manifold differential geometry.
In this paper, we propose a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
The proposed scheme offers a simple solution to the predictive quantization problem, which brings about ease of implementation, and improved performance as well, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations.

@@

\section{\textbf{System Model}}
\label{section2}
We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system. 
In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is denoted by:
\begin{equation}
\by_{i,t}=\bH^{H}_{i,t}\tilde{\bU}_{i,t}\bx_{i,t}+ \bw_{i,t}
\end{equation}
Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d. complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance. For this work, we assume that $\bH^{H}_{i,t}$ is estimated exactly, with zero error at the receiver.

@@

%Explain prediction and quantization steps here itself ! (succintly)
\section{\textbf{Reservoir model for Predictive Quantization}}
\label{section3}
\subsection{\textbf{Vectorizing matrices in Stiefel Manifold}}
\label{vectorize}
The reservoir computing framework has inputs and outputs as real vectors, and thus, it is necessary to convert the precoding matrices to vectors.
A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $\mathbb{C}^{N_T \times N_R}$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$.
For brevity, we call such a matrix $\mathcal{\bM}$ a `semi-unitary' matrix.
A na{\"i}ve method to vectorize a $\mathbb{C}^{N_T \times N_R}$ semi-unitary matrix would be to take all its $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$ property, which implies that each vector that represents the columns of $\mathcal{\bM}$ is orthogonal to the other columns.
For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
For the second column, we take only the first $N_T-1$ complex numbers and concatenate, since the last number can be determined by utilizing orthogonality with the first column.
For the third column, we take only the first $N_T-2$ complex numbers, and so on.
Therefore, we vectorize a $\mathbb{C}^{N_T \times N_R}$ semi-unitary matrix into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-N_R^2+N_R$ dimensional vector.

Observe here that we incur a dimensional penalty upon vectorizing semi-unitary matrices.
$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold, whereas we get a $2N_TN_R-N_R^2+N_R$ dimensional vector representation.
This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
It looks as if utilizing the norm 1 property, we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$. However, this would lead to non-unique representations, since there could then be infinite possible values that the lone missing complex number can take, so that the vector has unit norm. Hence, we vectorize a semi-unitary $\mathbb{C}^{N_T \times N_R}$ $\mathcal{\bM}$ into $2N_TN_R-N_R^2+N_R$ dimensional vector, denoted as $\bm$.
%Focus on the fact that you don't actually pay a penalty
%The thing to quantize remains on the Stiefel Manifold
\subsection{\textbf{Forward Prediction $f_P$ function}}
\noindent The vector representation of semi-unitary matrices allows to proceed with our discussion on reservoir computing framework.
Consider the reservoir computing framework in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic

@@

\subsection{\textbf{Quantization function $q_P$}}

@@

\subsection{\textbf{Reservoir Training Procedure, the backward pass}}

@@

The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate), gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.

@@

%\textcolor{blue}
{\noindent Another advantage of the proposed scheme is the ease of training the reservoir, captured in \eqref{res_upd}.
By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
Reservoir computing, thus proposes an easy to train data centric scheme, which is not typical for data centric ML based schemes.
}

\section{\textbf{Simulation Results}}
\label{section4}

\subsection{\textbf{Simulation setting considered}}
\label{setting}

@@

For predicting channels at each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}. Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ are initialized randomly, and $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
% All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with 
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/table.pdf}
\caption{The transmitter obtains feedback for $\{0,9,\ldots,63\}$ ($\{9k, k \in \{0,1,\ldots,7\}\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows. For each time instant, the transmitter uses the Cayley method to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ subcarriers.}
\label{table}
\vspace{5pt}
\end{figure}

\subsection{\textbf{Quantization error, BER and Achievable Rate Results}}
\label{res}{}
% To mitigate errors in prediction upon the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations, and the algorithm is re-starte.
\noindent Averaging is performed over 10 independent channel realizations, to ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile. Therefore, the quantization error, BER and achievable rate results are averaged over 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{images/qtizErr.pdf}
\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
\label{qtiz_err}
\vspace{-10pt}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.43\textwidth]{images/BER_res.pdf}
\vspace{-5pt}
\caption{BER results: Here, red curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter. The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available for each time instant, and non fed back precoders are interpolated via Cayley method. Observe that the proposed framework BER curve (provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over the work presented in \cite{6891198} (blue).}
\label{BER}
\end{figure}

@@

\section{\textbf{Conclusions and Future Work}}
\label{section5}

In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders.
The simulations reveal significant improvement in quantization error, BER, and achievable rate for IEEE Pedestrian-A channel model with normalized Doppler $10^{-4}$. 
The novelty enabling these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
If the simulation results hold in the hardware implementation, the proposed framework would be able to communicate at significantly lower power levels for the same BER, as illustrated in Fig. \ref{BER}.
Note that these results have been obtained by exploiting just the temporal correlations for predictive quantization, and can potentially improve if temporal-frequency correlations are exploited jointly.
This motivates further study into the reservoir framework, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
\vspace{-4pt}

>>>>

Precoding matrices obtained from SVD of the MIMO channel matrix (which is estimated at the receiver) can be utilized at the transmitter for optimum power allocation and lower BER transmissions. 
A key step enabling this improved performance is the feedback of these precoders to the transmitter from the receiver.
Since the bit budget for such Channel State Information (CSI) feedback is limited, these precoders need to be quantized effectively using just a few bits.
For a $N_T \times N_R$ MIMO system ($N_{\{T/R\}}$: Number of Transmit/Receive Antennas), this amounts to quantizing a $N_T \times N_R$ complex-valued matrix.
This task is aided by the presence of an underlying manifold structure and temporal/frequency correlations in the precoders. 
Predictive quantization methods reduce the quantization error by predicting new precoders based on observation of past precoders, and then quantizing the information required to obtain the actual precoder from the predicted value. 
In this work, we introduce a reservoir computing based framework for predictive quantization by exploiting temporal correlations. 
Past methods have primarily exploited the nonlinear geometry endowed by the manifold structure for precoder prediction.
Here, this non-linear relationship is captured using the dynamical reservoir state as part of the online training process of the reservoir.
Simulations reveal that this approach produces reduced quantization error, thereby resulting in lower BER as well as improved achievable rates when compared to earlier work.
\end{abstract}

\section{Introduction}
\label{intro}
% Broad summary of your work, come to your problem definition.
In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ antennas of the transmitter.
The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
Therefore, to obtain the said benefits of SVD precoders at the transmitter, the receiver needs to quantize and feed back the precoders it obtains from the SVD of MIMO channel matrix.
To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
Given the high dimensionality of precoders (which form a $N_T \times N_R$ complex-valued matrix, viz. $2N_TN_R$ real numbers), effective quantization with just a few bits poses a significant challenge.

% Elaborate on each point (what people have done before) lecunnas
Past work has used two inherent properties of the precoders to enable effective quantization with just a few bits.
First, the precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with lower dimensions, when performing operations over the manifold directly.
Second, these precoders are correlated in both time and frequency.
Utilizing these correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
This improvement is obtained because utilizing the correlations for estimation of the new precoder, allows for quantization of just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.
Combining the two inherent properties (viz. manifold structure and correlations), requires generalization of various well known linear algorithms for prediction, quantization and interpolation, to the manifold structure. This is done by exploiting the underlying non-linear differential geometry of the manifold. Relevant past work in this direction has been presented in \cite{Gupt1905:Predictive,6891198,6545375,5671092,Li2016,khaled2005quantized,krishnamachari2013geometry,chang2011adaptive}.

% What is the way ahead
Manifold based approaches for predictive quantization have provided significant performance benefits, given that they work with the effective lower dimensions while framing the manifold operations to predict and quantize.
However, these approaches are non-trivial, since they require specific operations over the non-linear manifold differential geometry.
In this paper, we aim to capture the above non-linear relations using a reservoir computing based predictive quantizer to exploit the temporal correlations effectively.
The proposed framework offers a simple solution to the predictive quantization problem, which brings about ease of implementation, along with improved performance, when compared to \cite{6891198}, which proposed a manifold based method of predictive quantization by exploiting temporal correlations as well.

@@

\section{System Model}
\label{section2}
We consider a point-to-point $N_T\times N_R$ MIMO-OFDM wireless system. 
In this discussion, we assume that $N_T > N_R$ and $N_s = N_R$.
The available bandwidth is divided into $N$ subcarriers, so that, individually for each subcarrier, the channel can be assumed to be flat fading.
Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is denoted by:
\begin{equation}
\by_{i,t}=\bH^{H}_{i,t}\tilde{\bU}_{i,t}\bx_{i,t}+ \bw_{i,t}
\end{equation}
Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d. complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance. For this work, we assume that $\bH^{H}_{i,t}$ is estimated exactly, with zero error at the receiver.

@@

%Explain prediction and quantization steps here itself ! (succintly)
\section{Reservoir Framework for Predictive Quantization}
\label{section3}
\subsection{Vectorizing matrices in Stiefel Manifold}
\label{vectorize}
The reservoir computing framework has inputs and outputs as real vectors, and thus, it is necessary to convert the precoding matrices to vectors.
A precoding matrix $\mathcal{\bM} \in \text{St}(N_T,N_R)$ is a $\mathbb{C}^{N_T \times N_R}$ matrix with the property $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$.
For brevity, we call such a matrix $\mathcal{\bM}$ a `semi-unitary' matrix.
A na{\"i}ve method to vectorize a $\mathbb{C}^{N_T \times N_R}$ semi-unitary matrix would be to take all its $N_TN_R$ complex numbers individually and stack them onto a $2N_TN_R$ dimensional real vector.
However, a more efficient approach would be to use the $\mathcal{\bM}^H\mathcal{\bM}=\text{\textbf{1}}_{N_R}$ property, which implies that each vector that represents the columns of $\mathcal{\bM}$ is orthogonal to the other columns.
For the first column, we take its $N_T$ complex numbers and stack them onto a $2N_T$ vector.
For the second column, we take only the first $N_T-1$ complex numbers and concatenate, since the last number can be determined by utilizing orthogonality with the first column.
For the third column, we take only the first $N_T-2$ complex numbers, and so on.
Therefore, we vectorize a $\mathbb{C}^{N_T \times N_R}$ semi-unitary matrix into a $2(N_T)+2(N_T-1)+\ldots+2(N_T-N_R+1)= 2N_TN_R-N_R^2+N_R$ dimensional vector.

Observe here that we incur a dimensional penalty upon vectorizing semi-unitary matrices.
$\mathcal{\bM} \in \text{St}(N_T,N_R)$, which is a $2N_TN_R-N_R^2$ dimensional manifold, whereas we get a $2N_TN_R-N_R^2+N_R$ dimensional vector representation.
This corresponds to an overhead of $N_R$ dimensions, since we have not exploited the fact that each of the $N_R$ column vectors is a unit norm vector as well.
It looks as if utilizing the norm 1 property, we could just take $N_T-1$ complex numbers when vectorizing the first column, instead of $N_T$. However, this would lead to non-unique representations, since there could then be infinite possible values that the lone missing complex number can take, so that the vector has unit norm. Hence, we vectorize a semi-unitary $\mathbb{C}^{N_T \times N_R}$ $\mathcal{\bM}$ into $2N_TN_R-N_R^2+N_R$ dimensional vector, denoted as $\bm$.
%Focus on the fact that you don't actually pay a penalty
%The thing to quantize remains on the Stiefel Manifold
\subsection{Forward Prediction $f_P$}
\noindent The vector representation of semi-unitary matrices allows to proceed with our discussion on reservoir computing framework.
Consider the reservoir computing framework in Fig. \ref{res_overview} %Ref Fig. Reservoir Pic

@@

\subsection{Quantization function $q_P$}

@@

\subsection{Reservoir Training Procedure, the backward pass}

@@

The key idea for reservoir training is that, as the predicted matrix $\bP_{i,t}$ (the coarse estimate) gets closer to $\tilde{\bU}_{i,t}$ (the refined estimate), the receiver has to quantize even smaller subspaces, and can thus provide a more refined estimate from the feedback $\text{fb}_{i,t}$.

@@

%\textcolor{blue}
{\noindent Another advantage of the proposed scheme is the ease of training the reservoir, captured in \eqref{res_upd}.
By storing just one matrix $\text{\textbf{num}}_{i,t}$ and a number $\text{den}_{i,t}$, we capture the entire history of the obtained quantized precoders, with past values weighted by $\lambda$ in $\mathcal{O}_{i,t}$ \eqref{oit}.
This is a departure from previous schemes \cite{Gupt1905:Predictive,6891198,6545375} which store the past $p$ precoders in a $p$ sized cyclic buffer ($p$ also has to be pre-decided).
Reservoir computing, thus proposes an easy to train data centric scheme, which is not typical for data centric ML based schemes.
}

\section{Simulation Results}
\label{section4}

\subsection{Simulation setting considered}
\label{setting}

@@

For predicting channels at each of the $8$ fed-back subcarriers, we consider $8$ separate reservoirs, each of them evolved separately, with $i\in\{9k, k \in \{0,1,\ldots,7\}\}$ in both the forward pass prediction and quantization ($f_P,q_P$) \eqref{fpqp} and backward pass to update $\bW_{i,t}^{\text{out}}$ \eqref{backpass}. Unlike \cite{Gupt1905:Predictive}, we do not exploit frequency correlations for predictive quantization, and the $8$ reservoirs for prediction of $8$ fed-back subcarriers are kept independent of each other.
All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with probability of edge connections being $0.2$, $\lambda=2$, $\bW^{\text{out/in}}_{i\in\{9k\},0}$ are initialized randomly, and $D_{\text{in}}=D_{\text{out}}=14$ (vectorized representation of $4\times2$ semi-unitary matrix, Section \ref{vectorize}) and $D_{\text{resv}}=60$.
% All these 8 reservoirs are initialized with $\bA_{i\in\{9k\}}$ being an Erdos-Reny\"i graph, with 
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/table.pdf}
\caption{The transmitter obtains feedback for $\{9k, k \in \{0,1,\ldots,7\}$ subcarriers, and uses $\tilde{\bU}_{i,t-1}$, along with $f_P,q_P$ \eqref{fpqp} to obtain $\tilde{\bU}_{i,t}$, illustrated in the figure via cyan arrows. For each time instant, the transmitter uses the Cayley method to interpolate $\tilde{\bU}_{i,t}$ at $i\neq\{9k\}$ non fed back subcarriers (green arrows).}
\label{table}
\vspace{5pt}
\end{figure}

\subsection{Quantization error, BER and Achievable Rate Results}
\label{res}{}
% To mitigate errors in prediction upon the presence of randomly appearing drastic events in wireless channels, such as sudden interferences and dynamic environments, only 100 channel evolutions are considered for the simulations, and the algorithm is re-starte.
\noindent To ensure that the simulation results hold in general for the chosen IEEE Pedestrian A channel profile, we perform averaging over 10 independent channel realizations. Therefore, the quantization error, BER and achievable rate results are averaged over 1000 channel instances, with 100 channel evolutions of 10 independent channel realizations.
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{images/qtizErr.pdf}
\caption{Quantization error in terms of chordal distance to the actual precoder $\bU_{\{9k\},t}$ observed at the receiver, from the quantized estimate $\tilde{\bU}_{\{9k\},t}$, averaged over 8 fed back subcarriers ($\{9k, k \in \{0,1,\ldots,7\}\}$) and 10 independent channel realizations (normalized Doppler $f_DT_s=10^{-4}$).}
\label{qtiz_err}
\vspace{-10pt}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.43\textwidth]{images/BER_res.pdf}
\vspace{-5pt}
\caption{BER results: Here, red curve is the most ideal case considering exact $\bU_{i,t}$ for all 64 subcarriers, at each time instant are available at the transmitter. The \{green/yellow/blue\} curves corresponds to the case in which \{$\bU_{9k,t}$/$\tilde{\bU}_{9k,t}$ from reservoir method/$\tilde{\bU}_{9k,t}$ from \cite{6891198}\} is available for each time instant, and non fed back precoders are interpolated via Cayley method. Observe that the proposed framework BER curve provides significant improvement in $\text{E}_\text{b}\text{N}_0$ levels over \cite{6891198} (normalized Doppler $f_DT_s=10^{-4}$).}
\vspace{5pt}
\label{BER}
\end{figure}

@@

\section{Conclusions and Future Work}
\label{section5}

In this paper, we have presented a reservoir computing framework for predictive quantization of SVD precoders by exploiting temporal correlations.
The simulations reveal significant improvement in quantization error, BER, and achievable rate for IEEE Pedestrian-A channel model with normalized Doppler $10^{-4}$. 
The novelty that enables these improvements lies in the training method for the reservoir framework, which refines the predicted coarse estimates as the reservoir evolves.
The simulation results indicate that the proposed framework would be able to communicate at significantly lower power levels for the same BER, as illustrated in Fig. \ref{BER}.
Note that these results have been obtained by exploiting just the temporal correlations for predictive quantization, and can potentially improve if temporal-frequency correlations are exploited jointly.
This motivates further study into the reservoir framework, and a detailed analysis of impact on performance caused by choice of different reservoir parameters like $\bA,\text{tanh}(\cdot),$ and $D_{\text{resv}}$.
\vspace{-4pt}
